WGS fastq2vcf walkthrough

### 2023-03-21 index02.Rmd
beta testing landing page layout

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
---
title: "Introduction"
---

# Guidelines for 'omics analyses

@@

Based on the expertise of the MarineOmics working group, the first topics include:

### Topics {.tabset .tabset-fade .tabset-pills}
#### Population Genomics

@@

#### Functional Genomics

@@

#### Genome-Phenome

* coming soon!

### {-}

### The guidelines portion of the website should be considered a "preprint". If you are interested in contributing to the peer review process, check out the [Discussion Forum](https://github.com/MarineOmics/marineomics.github.io/discussions). {.unlisted .unnumbered}

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
---
title: "Welcome"
---

@@

# Population Genomics

@@

# Functional Genomics

@@

# Genome-Phenome
* coming soon!
